Efficient spherical Convolutional Neural Networks with Healpix sampling for cosmological applications

### 2018-05-24 scnn.tex
writing intro + refs

% MATH SYMBOLS
\newcommand{\1}{\b{1}}              % all-ones vector
\newcommand{\0}{\b{0}}              % all-zero vector
\newcommand{\g}[1]{\b{#1}}
\renewcommand{\L}{\b{L}} % the laplacian matrix
\newcommand{\W}{\b{W}}
\newcommand{\I}{\b{I}}
\newcommand{\D}{\b{D}}
\newcommand{\U}{\b{U}}
\newcommand{\bLambda}{\b{\Lambda}}
\newcommand{\blambda}{\b{\lambda}}

@@

Cosmological data often comes in a form of spherical sky maps.
Observables such as the Cosmic Microwave Background (CMB) \citep{planck2015cosmologicalparameters,komatsu2011sevenyear,staggs2018recentdiscoveries}, neutral hydrogen \citep{santos2015cosmologySKA,HI4PI2016fullskyHI}, galaxy clustering \citep{alam2017clusteringgalaxies}, gravitational lensing \citep{troxel2017darkenergy,hildebrandt2017kidscosmological}, and others have been used to constrain cosmological models

Cite the following papers:
\begin{itemize}
    \item Healpix paper \citep{gorski2005healpix}
    \item First DES mass maps \citep{chang2017curvedsky}
    \item Healpix convolutions with asymetric beams \citep{mitra2011fastpixel}
    \item Mass mapping on the sphere \citep{wallis2017mappingdark}
    \item Wavelets on the sphere \citep{leistedt2016wavelet}
    \item Planck main result \citep{planck2015cosmologicalparameters,komatsu2011sevenyear}
    \item HI map \citep{HI4PI2016fullskyHI,}
    \item more radio maps from Adam+Hamsa \citep{santos2015cosmologySKA}
    \item more astro science on the sphere, what other survey make maps?
    \item alternative sampling on the sphere \citep{mcewen2011novelsampling} MW sampling
    \item cite kids tomographic power spectrum \citep{koehlinger2017kidstomographic}
\end{itemize}

>>>>

% MATH SYMBOLS
\newcommand{\1}{\b{1}}              % all-ones vector
\newcommand{\0}{\b{0}}              % all-zero vector
\newcommand{\g}[1]{\b{#1}}
\renewcommand{\L}{\b{L}} % the laplacian matrix
\newcommand{\W}{\b{W}}
\newcommand{\I}{\b{I}}
\newcommand{\D}{\b{D}}
\newcommand{\U}{\b{U}}
\newcommand{\bLambda}{\b{\Lambda}}
\newcommand{\blambda}{\b{\lambda}}
\newcommand{\pkg}[1]{\texttt{#1}}

@@

Cosmological and astrophysical data often comes in a form of spherical sky maps.
Observables such as the Cosmic Microwave Background (CMB) \citep{planck2015cosmologicalparameters,komatsu2011sevenyear,staggs2018recentdiscoveries}, neutral hydrogen \citep{santos2015cosmologySKA,HI4PI2016fullskyHI}, galaxy clustering \citep{alam2017clusteringgalaxies}, gravitational lensing \citep{troxel2017darkenergy,hildebrandt2017kidscosmological}, and others have been used to constrain cosmological and astrophysical models. Deep Learning methods have recently started to gain popularity as an analysis tool in cosmology \citep{schmelze2017cosmologicalmodel,luciesmith2018machinelearning,gupta2018nongaussianinformation,gillet2018deeplearning,hassan2018reionizationmodels,aragoncalvo2018classyfyinglarge,ciuca2017cnnstring}.
So far these algorithms have been demonstrated on the flat images.
Analysis of larger survey area in this form requires dividing the data into smaller chunks and projecting them on a flat, 2D surface.
While this process can work efficiently as already demonstrated, it may be more convenient do work with deep learning directly on the sphere.
The most commonly used scheme in astrophysics to divide a sphere into pixels is \pkg{Healpix} \citep{gorski2005healpix}, which uses pixels with the same area.

In this work we present an algorithm and software package to implement efficient deep convolutional neural networks on Healpix maps.

Cite the following papers:
\begin{itemize}
    \item Healpix paper \citep{gorski2005healpix}
    \item First DES mass maps \citep{chang2017curvedsky}
    \item Healpix convolutions with asymetric beams \citep{mitra2011fastpixel}
    \item Mass mapping on the sphere \citep{wallis2017mappingdark}
    \item Wavelets on the sphere \citep{leistedt2016wavelet} and ball \citep{leistedt2012exactwavelets}
    \item Planck main result \citep{planck2015cosmologicalparameters,komatsu2011sevenyear}
    \item HI map \citep{HI4PI2016fullskyHI,}
    \item more radio maps from Adam+Hamsa \citep{santos2015cosmologySKA}
    \item more astro science on the sphere, what other survey make maps?
    \item alternative sampling on the sphere \citep{mcewen2011novelsampling} MW sampling
    \item cite kids tomographic power spectrum \citep{koehlinger2017kidstomographic}
\end{itemize}
